\documentclass{gd-document}

\usepackage{xspace}

\newcommand\DrM{Dr.\,M.\xspace}
\newcommand\Azdhor{Lord Àzdhôr\xspace}

\newcommand\level[1]{\textit{#1}}

\begin{document}
\title{Proposal for a TSC Story}
\author{Marvin Gülker (Quintus)}
\date{2016-04-02}
\docnr{16/4}
\abstract{\noindent
  This is a proposal for a storyline in TSC. It features \DrM as
  the antagonist of the player, who finally realises his mistakes when
  his Right Hand \Azdhor betrays him. Includes a suggestion on a
  heroine.}

\maketitle{}

\tableofcontents

\section{dramatis personae}

\subsection{Alex}

The hero of the game, at least on the beginning. Somewhere around 20
years old. At the beginning of the game, he is a small criminal
(thief) without a nearer family.

\subsection{Akan Albin}

Heroine of the game; appears later in World 3. Most of her family has
died during a military conquest of \DrM (who wanted both to find a
volume of the Chronicles and paralyse is enemy Thomas Albin), except
for her grandfather Thomas (see \ref{sec:thomas} below), with whom she
lived before he sent her out for defeating \DrM’s quest for the
Chronicles. About the same age as Alex.

\subsection{\DrM}

\DrM is the antagonist of the game. He is an old man of originally
nobel character, but has a burning desire for knowledge. He is the
heir and Protector of the Great Library, and in search of the Secret
Chronicles which he believes to be the route to complete wisdom. After
he collected 3 of the 12 volumes of the Secret Chronicles, the evil
aura of these works makes him ruthless in his quest, kicking out of
his way whomever he deems to be against his search of wisdom.

\subsection{\Azdhor}

He is the Right Hand of \DrM. An arch-evil enemy who stops for nobody
and nothing to reach his goals. He has observed that the owner of the
Secret Chronicles is the possesor of great power that can be used to
rule over everyone. He joined \DrM only to have him and his influence
help him to find the Chronicles, and he is secretly planning to
overthrow \DrM as soon as all volumes of the Chronicles are found.

\DrM does know nothing about \Azdhor’s secret plans and believes him
to be truly loyal, albeit a little rude.

\subsection{Gereon}

An old mage, friend of Alex.

\subsection{Thomas Albin, Count of Albermore}\label{sec:thomas}

This person never actually appears in the game. He is owner of a great
area of land, and is perceived by \DrM as his main enemy. He is an old
man unable to walk on his own and a distant relative of \DrM, and long
ago one of his (and \DrM’s, i.e. before the family branches divided)
ancestors once was the Protector of the Great Library. In his family,
the danger of the Secret Chronicles has been preserved and as soon as
he noticed \DrM’s quest for finding the Chronicles, he sent out the
last heir of his family, Akan, to counter \DrM’s intents, by
collecting the volumes of the Chronicles and destroying them.

\section{The scene}

A fantasy land, developed somewhere between the Middle Ages and the
Industrial Age. People know what machines are, but their use is rather
rare; government is formed by a king still, but the time of knights is
definitely over. There is a basically working police and court system
in place. The press has started its work.

There exists magic in this world, but not known by many people and
generally its use is forbidden.

The capital of this fantasy land is Albermore, and this is where the
story starts. Outside of cities, monsters like furballs, armys,
etc. endanger the land.

\section{Story}

\subsection{General Notes}

During the story, several references to well-known literature should
be made. \DrM is quoting Shakespeare all the time, and at sites like
the City of the Ancients one could make some subtle references to the
Ilias or even Gilgamesh. There shouldn’t be blatant copies, though.

Notice the frequent appearance of the number 12. 12 worlds, 12 levels,
12 volumes. This is intentional as 12 is a number used by a good
number of mythologic tradition.

During the course of the game there should every now and then be press
articles outlining that Alex is searched for. They could also contain
other story-related news, or something completely unrelated to the
main story as a side note.

\subsection{World 0. Prologue.}

[cutscene]
Alex is a small criminal. As a mostly illeterate thief he lives from
what he has stolen here and there, and occasionally he finds a way
through an open window or forgotten door into a house. He is known by
the police forces, but usually skilled enough to not be cought.

One night he manages to break into the villa of some rich individual,
but to his great disgust, he does not find anything that looks
evidentally valuable to him. There is no money lying around, and the
valuable furniture is too heavy to steal quickly. He wanders around
and finds that this rich indivual has some books lying around that at
least look a little as if they could be of some value. Before he can
take a closer look at them, he hears moves in the floor above, thus
takes the books off the shelf and flees uncought.

In his hiding place he places the books among his other stolen pieces,
but then forgets about them in the following days as he does not know
anybody who could be interested. Then strange things start to
happen. On one of his journeys through the streets he is nearly hit by
falling bricks; another day he notices some person following him all
the time. In a park where he uses to sell his stolen goods he finds a
letter with his name on it saying “Hand the Chronicles over to me
tomorrow at this time at this place.”. In fear he does not follow that
command, and a few days later he nearly got victim of a brutal
robbing. He starts wondering about what these “Chronicles” are, then
remembers the theft at the rich man’s house and these worthless
books. Back at his hiding, he finds these books are still there. Three
of them look harmless, but the fourth is a richly decorated blue
volume with gold decorations, whose script appears to be of a foreign
language that he cannot read. He concludes that this must be the
“Chronicles” the unknown person requested from him. Being a
commercially thinking person, he finds that this book must be of utter
importance for someone, but in order to be able to request a high
price for it, he must know more. He decides to visit Gereon, an old
man who has been a criminal in his younger days as well. He knows
Gereon is a person who has always been interested in mystic stuff and
exercies the forbidden practise of magic.

The next day he wakes up he finds police forces in front of his
door. He has no idea how they found his hiding place, but thinks it is
possible it might have to do with this mysterious book he has. As a
good criminal, he takes a secret exit from his hiding place and heads
hastily towards the forest outside of Albermore, which is where Gereon
lives deep inside.
[/cutscene]


\level{Level 1. Flight.}

A city level with mild time constraint. Alex wants to escape the
police forces. The level ends at the edge of the forest.

\level{Level 2. Forest.}

Alex on his way to Gereon’s hidden home in the forest. Level ends
there.

[cutscene]
Alex shows Gereon his mysterious book, but Gereon cannot make much of
it. After some thinking, he tells Alex an old story he has heard of
during his journeys, in which there are 12 books of the Secret
Chronicles, who set their owner into the ability of gaining absolute
knowledge about the world. It might be possible they even include the
key to eternal life, however, the books, if collected in larger
amounts, are said to have an evil aura influencing their possesor
towards the evil. Thus, the Ancient People who has wrote these
Chronicles have decided to hide them separately all over the land,
such that they might only be found when the time has come mankind can
handle them. For the time being, they erected the Great Library, place
of eternal wisdom, whose Protector has knowledge about the hiding
places and has the duty to shield mankind from the Chronicle’s
influence until the time has come. Ages have passed since that time;
the Ancient People is extinct (only ruins of their city exist), and
about the Great Library there are only rumours left. The only hint
given in the story is that the Great Library is hidden deep in the
southern jungles of the land.

Alex is baffled by the story he has innocently been drawn into. Now
he likely has one of those twelve Chronicles in his hands, a dangerous
tool for mankind. His intention to sell it to the person who requested
it has vanished; it is likely that this person has no good intentions
with that powerful tool. Instead, he decides, the book must be brought
to the Protector of the Great Library. Gereon wishes him good luck,
and to circumvent the police still in search for Alex, he shows them a
secret tunnel that leads outside the forest.
[/cutscene]

[ Actually, the person requesting the book was \DrM. This is not
mentioned explicitely from the story, but becomes clear from what
happens. ]

\level{Level 3. Tunnel.}

Simply underground level ending with an exit outside the forest.

\subsection{World 1. The Jungle.}

\level{Some jungle levels here. Later levels with bookshelfs
  somewhere, to indicate Alex is reaching the Great Library.}

\level{Last Level. The Great Library}

A short jungle period, then the path widens and Alex stands before the
main entrance of the Great Library.

[cutscene]
Alex is asked for what he wants at this secret place nobody knows. He
reveals his possession of one of the volumes of the Chronicles,
resulting in him being taken through the main entrance and some
corridors directly to \DrM’s working room.

At his first enountering with \DrM, \DrM acts as a nice person. He
introduces himself as the Protector of the Great Library and
explicitely thanks Alex for his efforts to bring the volume to him. He
confirms that the story of the Ancients, the Library, and his
protection duty is true, and tells him that for best execution of his
duties he needs to obtain possession of all 12 volumes. Thereby he
notes that he has already been able to find 3 existing ones.

[ In reality, the 3 volumes \DrM has obtained already have infected
his mind. He has become a man striving for the absolute wisdom,
believing that he is the saviour of mankind if he manages to find and
understand all the Chronicles. Anybody who is standing in his way gets
eliminated. At this point, he just thinks Alex can be of use for him,
so he tries to include him into his quest. ]

\DrM also talkes about the Count of Albermore, whom he depicts as his
enemy. He makes Alex think that this person wants to obtain the
volumes just for the sake of power and subjugation, and that he has to
be aware at any time that spies of the Count might try to convince him
from the contrary.

Lastly, \DrM introduces him to \Azdhor, his Right Hand and tells him
to hand any volumes he finds to him if \DrM himself is not reachable
at that time. Alex finds \Azdhor very, very unsympathic from the very
beginning.

\DrM now sends out Alex as his agent in the quest for searching the
Chronicles.
[/cutscene]

\subsection{World 2. The Plains}

\level{Several levels...}

Last level ends with finding another volume.

\subsection{World 3. The Mountains}

\level{Several levels...}

After the last level’s boss, Alex finds another volume.

[cutscene]
Before he can leave, Akon appears. She is too late, as Alex has
already set himself into position of the volume. A dispute arises
where she identifiers herself as being sent by the Count of Albermore
and tries to convince him from \DrM’s real intentions. Remembering
\DrM’s warnings against the Count, he does not believe her; before the
dispute can continue, \Azdhor shows up and attacks Akon, who flees. He
asks Alex rudely to hand over the two found volumes, and after having
received them, he sends him to the City of the Ancients, where he says
\DrM expects another volume to be hidden.

\subsection{World 4. The City of the Ancients.}

This world is the turning point in the story.

\level{Level 1-4 normal ruin levels.}

\level{Level 5. The Ancient Temple.}

At the end of this level (preferably in a catacomb where nobody can
escape easily) Alex meets Akon again. This time, Akon tells him about
the military conquests \DrM has done in search for the Chronicles, and
in tears reports the death of most of her family as a result. Alex
this time believes her, and from this point on both strive to stop
\DrM. Alex feels miserable as he recognises his mistake.

She tells Alex that \DrM has not been successful with his conquest
against her family; the two volumes in their possession have been
hidden by the Count in his younger years. She knows the hiding places,
but there is also a strong hint that one volume never left the City of
the Ancients, which is confirmed by \Azdhor’s command to Alex to
search for it here.

[ At this time, both believe \DrM has now obtained possesion of 6
volumes. In reality \Azdhor never handed the two volumes he got from
Alex to \DrM, \DrM does not know that. That is, \DrM at this point
still has only 4 volumes. ]

\level{Further levels, with a volume being found at the end of
  the last level.}

[ At this point, \DrM has 4 volumes, \Azdhor 2, Alex and Akon 1 ]

\subsection{World 5. (no topic set yet)}

\level{Several ordinary levels.}

[cutscene]
At the last level, they encounter \DrM who just set himself into
posession of the volume of this world. He immediately notices Akon
next to Alex and understands he lost his influence on Alex. With
\Azdhor protecting him, he leaves, indicating in a half-heard sentence
something like “I will get the three volumes you still have as
well!”.

[ This is a hint that \DrM thinks the two volumes \Azdhor has are
still with Alex and Akon. ]
[/cutscene]

[ At this point, \DrM has 5 volumes, \Azdhor 2, Alex and Akon 1 ]

\subsection{World 6. (no topic set yet)}

\level{Regular levels, with a volume being found at the end.}

During the course of this world (but not narrated; it can be concluded
from what happens next) \Azdhor finds another volume and hides it in
the Monster Factory, which is basically for him what the Great Library
is for \DrM: The main operation point.

[ \DrM: 5 volumes. \Azdhor 3, Alex and Akon 2 ]

\subsection{World 7. \DrM’s ship.}

\level{Regular levels.}

The boss of this world is \Azdhor. When defeated, however, he
escapes. After the boss fight, they find \Azdhor’s two volumes,
i.e. those that Alex earlier handed to \Azdhor.

[ \DrM: 5 volumes, \Azdhor 1, Alex and Akon 4 ]

\subsection{World 8. (no topic set yet)}

\level{Regular levels.}

At the end Alex and Akon find that the volume hidden here is
gone. \DrM has been here earlier.

[ \DrM: 6 volumes, \Azdhor 1, Alex and Akon 4 ]

\subsection{World 9. The Monster Factory.}

\level{Regular levels. After the boss \Azdhor’s hidden volume is
  found.}

[ \DrM: 6 volumes, \Azdhor 0, Alex and Akon 5 ]

\subsection{World 10. Albermore.}

The quest ends where it started. In multiple levels in this world the
police shows up again and tries to arrest Alex, while they search
through several buildings in the city for the last volume.

\level{Level 1-5, some are time levels as Alex escapes the police.}

\level{Level 6. In this level, Alex gets finally arrested by
  police. Akon must play alone the next levels.}

\level{Level7-9 Normal levels.}

\level{Level 10. The Museum of History. In this museum, Akon finds the
  last volume without a boss fight.}

\level{Level 11. Free Alex! Tunnel level leading to the arrest cells
  of the Albermore police station. Level is played both forward (Akon
  alone) and backward again (now with Alex and Akon).}

[cutscene]
\DrM at the police station, looking at the escape tunnel, very upset.
[/cutscene]

[ \DrM: 6 volumes, \Azdhor 0, Alex and Akon 6 ]

\subsection{World 11. The Great Library.}

\level{Level 1. Side entrance.}

\level{More levels...}

\level{Level 11. The Chronicles Room.}

In this room \DrM keeps his volumes of the Chronicles. Akon and Alex
take them all and feel a little strange about this now.

[ \DrM: 0 volumes, \Azdhor 0, Alex and Akon 12 ]

\level{Level 12. \DrM’s working room.}

Expecting the great showdown.

[cutscene]
Alex and Akon enter \DrM’s working room. Both \DrM and \Azdhor are
there, debating over the topic of the volumes. Alex and Akon show
they’re in possession of all 12 volumes. They demand that the two give
up and leave the library immediately. Now something unexpected
happens. \Azdhor realises that \DrM is of no use anymore for him. He
takes him as hostage and threatens to kill him if he is not handed the
Chronicles. In this moment, \DrM simply looks like a desparate old man
who barely realises what is happening around him; Alex and Akon hand
the volumes over finally. \Azdhor frees \DrM and leaves the library.

\DrM is heavily shocked about what has happened. He realises the
Chronicles are gone, and are with \Azdhor. Sinking into a nearby chair
he slowly thinks through all that happened during his quest for the
Chronicles, and that now, in the last moment, he has been betrayed by
a person he truly believed to be loyal to him. Long silence.

Finally \DrM approaches our heroes. He announces that he from now on
will live up to the duty has has as the Protector of the Great
Library, and that he was tempted by the Chronicles. He assures he will
never again fall into this temptation, and says that it now is on him
to prevent the evil \Azdhor from causing severe damage with the
Chronicles. He reveals that the Ancient language that Chronicles are
written in has not yet been deciphered by him and \Azdhor, so that
there is some time left to stop him. Furthermore, he says that he
expects \Azdhor to have returned to his cloud castle, where they must
now go.
[/cutscene]

[ \DrM becomes playable at this point ]

\subsection{World 12. Cloud world.}

\level{Level 1. The Staircase Tower. A level with many, many, many
  stairs.}

\level{Cloud levels...}

\level{Level 12. The Cloud Castle.}

This level has \Azdhor as boss.

[cutscene]
After \Azdhor is defeated, \DrM immediately burns all 12 volumes of
the Chronicles. “They shall cause evil nevermore!”

However, as soon as the books are burned, the prophecy strikes
back. It was the duty of the Protector of the Great Library to
preserve and protect them until the time for them has come, not to
destroy them — \DrM dies at this point. The Great Library vanishes.
[/cutscene]

\section{Epilogue}

Back in Albermore, Alex again gets arrested by police for his crimes
as thief. However, mysteriously all data about his thefts has
disappeared. In court, he must be relased due to lack of proofs.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
