\documentclass{gd-document}

\begin{document}
\title{The Secret Chronicles of Dr. M Story Development Document - Version 2}
\author{Chris Jacobsen}
\date{2016-03-27}
\docnr{16/3}
\abstract{\noindent
  [ A story proposal by datahead, depicting Dr.\,M. as the heir of the
  Great Library, who likes to make Shakespeare quotes.\\-- note by
  Quintus ]

  [This proposal actually predates DNr. 16/1, but was included into
  the document repository later for technical reasons.\\
  -- note by Quintus]}
\maketitle{}

\tableofcontents

\section{Story}

Alex pushed through the foliage in the Amazonian rain forest. Sniffing
the air, he winced -- it almost seemed to stink. He grabbed a thick
layer of meshed vines and leaves and peeled it away, finding a yellow
shaped stone. Peeling more away, he discovered a grid work of stones,
forming a much larger wall.

"So it's true . . ." he said. "That old man wasn't lying when he
talked about the golden ruby . . . This could be the greatest artifact
ever discovered."

He spent the next hour peeling away more and more growth. He finally
found an opening in the foliage to the right, allowing him to maneuver
to a perpendicular side of the mysterious wall. He stepped onto the
soft soil of the rain forest and glanced upward to get a better view
of the structure. It was an ancient pyramid, but it did not look like
any Mayan or Aztec structure with which he was familiar. A dark
opening lay at the bottom.

Alex stepped into the opening, turning on his flashlight. He was
surprised, however at what he saw. It was a library, with bookshelves
lining the walls and dusty books neatly lying in rows.

Stepping past row after row of books, he soon saw a glimmer of
light. Stepping through the hole he found himself in a strange world
with vicious, furry creatures moving in the distance and wooden crates
that floated in the air.

"Who are you?" asked a voice.

Alex turned his head. "I'm Alex," he answered. "I stepped into a
library and found myself here . . ."

"You need to hide, lest the armies find you." Alex glanced at the
speaker, seeing a creature in the general shape of a fox, with dark
speckled fur and ears that seemed to curl back. "Dr. M is tearing
apart the cities. He thinks someone has the Chronicles."

Alex stared at him in confusion. "Who is Dr. M, and why does he want a
set of chronicles?"

"They are the Malevolent Chronicles," answered the fox creature. "They
are the final, missing piece of his collection. With them he will have
the power to rule this world."

Alex narrowed his eyes angrily. "Has no one stood up to this 'Dr. M'?"
he asked. "No one should be subjected to this kind of treatment."

"He has an army of monsters under his command and a factory to make
more of them," explained the fox creature. "Besides that, many people
actually respect him."

"Why would anyone respect a person like that?" asked Alex.

"Because he is the heir to the Great Library, the keeper of the books,
and his Ph.D. dissertation is one of the most respected in the land."

Alex nodded his head slowly. "Many dictators have had a cult
following; he sounds no different. If he's using the threat of
violence to control people, though, someone needs to stand up to him."

At that moment, a furball, with brown colored fur and bulging eyes
approached them. The fox person stepped back, clearly startled. Alex
took a deep breath, ran forward, and leapt upwards toward the monster,
his fist in the air.

\section{Characters}

\subsection{Alex}

he is the hero in the game. At the age of twenty two, he has been a
recreational treasure hunter for several years.

\subsection{Dr. Malus}

Abbreviated form: Dr. M - He is the villain in the game, an eccentric
librarian. He has headquartered himself in the Great Library, from
which he oversees the production and deployment of armies of monsters
as he searches for "The Malevolent Chronicles" - the final piece
missing from his personal collection of chronicles. Quoting
Shakespeare while traversing the world, he poses an unusual threat.

\subsection{Lord Vodo}

A major overlord who resiliently serves Dr. M.

\section{Locations}

\subsection{Faythe}

The home country of the Faythian fox people. These people are
downtrodden by Dr. M and simply want an undisturbed existence. Alex
befriends them and receives resources to bring the fight to Dr. M.

\begin{description}
\item[The cities:] Urban, skyscraper filled cities where the majority
  of the Faythians live
\item[The country side:] rural areas surrounding the cities
\end{description}

\subsection{The expanse}

unpopulated areas, with many elements ranging from deserts to frozen
tundra to forests to plains.

\subsection{The Great Library}

Dr. M's headquarters, commandeered from the library of the ancients.

\begin{description}
\item[Upper tier:] a room filled with paintings, chandeliers, and a
  balcony by which Dr. M can oversee the land below
\item[The stacks:]  Floor after floor with column after column
  of...BOOKS
\item[The Secret Chronicles Room:] Dr. M's collection of chronicles -
  the namesake of the game.
\item[Elevator System:] Old fashioned elevators with minimal
  electrical systems (if any at all)
\item[Defense Station:] An armed monster outpost intended to fend off intruders.
\end{description}

\subsection{The City of the Ancients}

The ruins of the ancient civilization surrounding the Great Library

\subsection{The Monster Factory}

The factory responsible for the production of Dr. M's monster armies.

\begin{description}
\item[Assembly lines:] Various kinds of monsters are assembled on
  conveyor belts using robotic systems.
\item[Waste Disposal System:] Factory waste is processed and purged
  here.
\item[Elevator System:] A mechanized, high tech elevator system
\item[Control Center:]
\item[Factory Operations:] Oversees running of the factory
\item[R \& D (Research and Development):] Oversees the development of
new technologies. 

\begin{description}
\item[Genetics and/or Magic Research:] Oversees the creation of new
  monsters, weapons, and other technologies
\item[Super Computing Station:] Mathematical simulations and other
  data crunching are executed here. The outside room is filled with
  computer monitors showing data/scientific visualizations.
\end{description}
\end{description}

\subsection{Monster Outpost}

A fortified, military monster position, with a series of connected
fortresses.

\subsection{Dr. M's ship}

A large ocean faring ship owned by Dr. M with firepower,
mechanization, and computing facilities.

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
