\documentclass{gd-document}

\begin{document}
\title{Unofficial Story Development Document}
\author{danfun64}
\date{2015-04-04}
\docnr{16/1}
\abstract{\noindent
  [ This is the second draft of danfun64’s story document proposal. It
  outlines a dark story around Alex, Dr. M., Lord Ázdhôr and the
  mesmo slugs, which turn their victims into zombies. It features
  multiple different endings. -- note by Quintus ]

  The faythians don't know much about the dark lord, whom I still
  haven't named yet. That's why in some of the endings, they welcome
  his taking over from Dr. M with open arms. Yes, Dr. M lives in some
  of the bad endings, and it is implied that he lives in the good
  ending. I also spared the lives of Haakon and his parents, and
  explained why he is sour and why he isn't playable in the second
  campaign.}

\maketitle{}

\tableofcontents

\section{Characters}

\subsection{Alex}

Human. Our hero. At 9 years of age, he isn't the most mature person in
the world. His parents were colonists of a land not unlike Central
America. The last thing he received from his parents was a
jewel. After they died when he was 6, it was discovered that he had no
living relatives in the continent. He went around the land, looking
for food and jewels, both of which he was obsessed with. While he has
a strange view of life, and may seem too happy and childish at times,
he is a good person, and is willing to fight the forces of
Dr. M. Playable on all campaigns. Wears red clothing.

\subsection{Deepak}

A wise, old Faythian with gray fur. He managed to reverse engineer
Dr.M's pipe system and make his own pipes, which lead to safe houses
across the land. He is the one who brought Alex to the land of Faythe,
and who gave him the quest to defeat Dr. M. Grandfather of Prewitt and
Haakon, and step-father to Helen.

\subsection{Helen}

Human. A girl with long, blonde hair not much older than Alex, and
much more mature and grounded in reality than he is. She was taken in
by Deepak a couple years before Alex was, but unlike Alex, managed to
live a normal life before their meeting. An excellent escape artist,
she could never remain captured for more than an hour. In fact,
sometimes she lets herself get captured in order to gain
information. Wears Blue clothing. Playable on all campaigns.

\subsection{Prewitt}

Yellow-furred twin of Haakon. One of the few courageous members of his
species. Highly curious of the world around him, it is implied that he
will grow up to be as intelligent as his grandfather. Playable on all
campaigns.

\subsection{Haakon}

Green-furred twin of Prewitt. The only reason he helps Alex, Helen and
Prewitt is because his grandfather said it was necessary. After the
events of the first campaign, he stops being playable.

\subsection{Dr. Malus/Dr. M.}

Human. The main villain of the story, an eccentric librarian. A
strange man, considered as intelligent as Father Fox. His true
intentions are indecipherable, and his views of right and wrong are
unintelligible. It is very difficult to tell if he is truly evil, or
if he is a paranoid man who wants to be left alone. He has
headquartered himself in the Great Library, from which he oversees the
production and deployment of armies of monsters as he searches for
"The Malevolent Chronicles" - the final piece missing from his
personal collection of chronicles.

\subsection{Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon (name to be
  determined from this list)}

Considered more clear cut evil than his master, Dr M. He is also
willing to do things that disturb Dr. M. Extremely dangerous, and very
hard to defeat. Despite his methods, Dr. M keeps him around as his
right hand man. May or may not be the son of Deepak and the father of
Prewitt and Haakon. If he is, however, he didn't become evil by
brainwashing, but made a conscious decision to aid Dr. Malus in his
quest for the Chronicles.

\subsection{Gage}

A clone of Alex created by Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord
Kodon. He is the product of a blood sample left behind when Alex gets
injured by a boss. Was implanted with a brain parasite which drained
him of his free will, then rapidly aged from baby to around the same
age Alex is. Unlike Alex's red clothing and brownish hair, Gage has
green clothing and brownish-red hair. The parasite causes him to
mindlessly serve his lord, giving him headaches and mild seizure-esque
effects if he even attempts to think for himself. Indirectly, his name
comes from Alex, who asks him what his name is when they first
meet. All he says is the command that Lord Ázdhôr/Lord Vodox/Lord
Zodo/Lord Kodon gives him, to “engage the enemy”. A little later in
the game, Alex manages to incapacitate him and take him to one of the
safehouses. There, Deepak makes a special potion allowing Alex to
enter his body, which is to be one of the worlds, in which the
parasite is the world's boss. After Gage is freed from the parasite,
his initial state remains emotionless and submissive, but eventually
his humanity comes to him and he starts thinking for himself. Even
after this, he is seldom happy, although he has infrequent moments of
warmth and smiling. Becomes playable after the first campaign,
replacing Haakon.

\section{Normal Species}

\subsection{Humans}

\subsection{Faythians}

A fox-like species at the other end of the first pipe Alex sees. They
are the natives of Faythe, a land far from Alex's “home”. They are
being persecuted by the forces of Dr.M and would fight them, if most
of them weren't cowards who don't know how to fight. What they lack in
courage, they make up for in ingenuity, having placed berry blocks in
their land long before they even heard of Dr M.

\subsection{Furrballs}

Mindless fuzzy creature that roam the land. Cute at first, but they
are friends to nobody.

\subsection{Armadillo Army}

Unlike their Furrball counterparts, they are more intelligent. While
most are loyal to Dr. M, some have rebelled, though you don't see it
in the game.

\section{The Mesmos}

\subsection{Mesmo Slugs}

Parasitic creatures that drain emotion and free will from the
brain. The best results can be achieved by putting the slug directly
on the brain, which is what Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord
Kodon does to Gage. If the slug is on the brain for an extended period
of time, it eventually eats the brain and replaces it, killing the
victim and turning it into a mindless zombie. This happens to Gage
only in the Living Gage Bad Ending. It is possible to remove the slug,
and if it removed completely (like what will happen to Gage) then the
victims body and mind will return to normal. However, if most of it is
removed but small bits remain, the victim may regain their free will,
but will be incredibly easy to hypnotize. The venom of the Mesmo Snake
strengthens Mesmo Slugs, and actually causes partially removed Mesmo
Slugs to regrow and regain complete control of their victim.

\subsection{Mesmo Snakes}

Getting bit by one causes victims to lose their free will for a few
hours, but the effect is temporary. It isn't shown in the game, but if
someone has a Mesmo Slug removed and the removal is only partial, the
venom will revive the slug and cause it to regenerate.

Wild Mesmo Snakes: The only difference between the bite of a Wild
Mesmo Snake and a “domesticated” one is that the venom of a Wild Mesmo
Snake causes its tribe to control the victim, while the venom of its
“tamed” variety only removes free will. The effects of both venoms
last only a short time.

\subsection{Wild Mesmo Spiders}

Large creatures with the size of a teenagers head. The hunters of Wild
Mesmo tribes. They look for victims of any non Mesmo species that are
large enough. When one of them finds a victim, it crawls to the
victims head and attaches itself. It then sticks two appendages onto
the victim's ears, where venom is injected. This is to pacify the
victim while it commences its next stage of attack. It then attempts
to drill a hole into the victim's head so it can place a Wild Mesmo
Slug into the victim's brain. If this fails (the drill isn't that
strong, so the skull has to be soft. It might be able to drill into a
human baby, but not an older human that doesn't have some sort of soft
skull disease) than it just plants a Wild Mesmo Slug onto the victim's
head. After a while, the slug starts to go to the back of the victim's
neck and harden itself. It is possible to cut off the slug from the
necks of victims, but first you would have to rescue them from the
protection of the Wild Mesmo tribe's hive mind, dragging them away
from others in their castes. When a Wild Mesmo Slug in implanted in
the victim either by the drill or outer attachment, it leaves to
search for a new victim.

\subsection{Wild Mesmo Zombies}

The victims of a Wild Mesmo Slug. While victim's of a “domsesticated”
Mesmo Slug retain their intelligence and language, Wild Mesmo Zombies
are reduced to animal intelligence, possibly because the Mesmo species
are animals themselves. After a couple hours of having a Wild Mesmo
Slug attached to them, they grow two antennae in their heads. The tips
have a specific color on them, representing their tribe. If one cuts
off the antennae but leaves the Wild Mesmo Slug intact, then the Slug
will just grow a new set of antennae. If one does the reverse, cutting
off the slug but keeping the antennae, the result is similar to having
a slug only partially removed, in that their free will returns, but
they become incredibly weak willed. There is one difference,
however. The antennae will cause the victim to sense when other beings
of the same tribe are near, and Wild Mesmo Snakes of the same tribe
will never stop hunting that being until it bites it, causing a new
Wild Mesmo Slug to appear where the previous one was removed.

\subsection{Wild Mesmo Queen}

The leader of the Wild Mesmo tribe Hive Mind. It controls its subjects
and puts them into castes: Itself on the top, Wild Mesmo Zombies on
the bottom, and the other Wild Mesmo species in the middle. It
resembles a Wild Mesmo Spider, but looks slimmer and has a huge
antennae on its head with the color of its tribe. When it lays eggs,
it takes a random Wild Mesmo Zombie and forces it to swallow the
eggs. The eggs then hatch and the babies eat the insides of the victim
until they come out. The Wild Mesmo Queen is surprisingly versatile in
what it can lay, laying eggs of multiple species. The two main ones
are Wild Mesmo Snakes and Wild Mesmo Spiders. Near the end of its
life, it stops laying eggs of those types and instead lays Wild Mesmo
Queen eggs. When those eggs hatch, instead of eating the victim right
away, they eat each other. The survivor then eats its way of of the
victim, heads for the Queen, and eats it, taking over as the leader of
the Hive Mind. If the queen dies without being replaced, her Zombies
go into comas until the Slugs are removed from them, while the other
species collapse and die. It is possible for the Queen of one tribe to
be eaten by the Queen of another tribe. When this happens, the two
colors of the two tribes merge and the Queen takes over both
tribes. The text of the Malevolent Chronicles states a way that
sentient beings can eat Queens and become rulers of Wild Mesmo Tribes,
which becomes a plot point in the second campaign. when Lord
Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon attempts this. The result of
successfully doing so is that the one who eats the Queen grows
antennae, like Mesmo Zombies. However, they also grow a large antennae
on the back of their neck. The intelligence of Wild Mesmo Zombies
returns to normal capacity, but still remain slaves.

\section{Backstory}

Our story begins in a land not unlike Earth. The sounds of many
strange animals whistled in the air. Suddenly, a loud cry of surprise
and anger. A deafening pounding could be heard as the natives chase a
young boy. Every single one of them recognized their enemy, for the
child has stolen many priceless gems and several pounds worth of their
sacred fruits. Another tribe from a great distance tried to raise him
after his parents died, but he was untamable. Dozens of jewels from
dozens of tribes were stolen by this kid, and his most recent theft
has made him hated by yet another one. “ALLLEEEEEEEEXXX!” the native
chief shouted as his men chased the boy. While Alex knew that he upset
the locals, he didn't completely understand why. All he cared about
was the beauty of his most recent prize. Despite carrying all of his
stolen valuables in a bag, he managed to run fast enough to hide in a
large cave. As he enters he notices a floating wooden block.

Tutorial\textunderscore{}level\textunderscore{}1:

(Based off the first half of the current tutorial level, the split
occupying around the area where Alex falls.) Alex hits the block with
his fist. A booming voice instructs him to climb up, using the gems on
the ground as a guide. He climbs higher and higher, until he notices a
platform floating in the air. He jumps on it, but it falls down. 

[CUTSCENE] When he lands, he notices a grid work of yellow stones,
forming a much larger wall. The child's eyes widen at their
beauty. “C-C-C-Could it be?” He asked nervously to no one in
particular. He pulls out a book entitled “The rare gems of the land of
*insert name here*”, one of the only reasons he still knows
English/Basic/*insert name here*, and flips through the pages until he
finds what he was looking for.

“So it's true . . .” he said. “That old man wasn't lying when he
talked about the golden rubies . . . .” He stares in awe at the
jewels, for what felt like hours, until he heard a loud scream
nearby. Cautiously, he walked to the direction where he heard the
sound, until he notices a pipe with a large open hole in
it. [/CUTSCENE]

Tutorial\textunderscore{}level\textunderscore{}2:

[CUTSCENE] Stepping through the hole he found himself in a strange
world with vicious, furry creatures moving in the distance and more
wooden crates that floated in the air.  “Who are you?” asked a voice.

Alex turned his head. “I'm Alex,” he answered. “I stepped into a pipe
and found myself here . . .”

“You need to hide, lest the armies find you.” Alex glanced at the
speaker, seeing a creature in the general shape of a fox, with gray
fur and ears that seemed to curl back. “Dr. M is tearing apart the
cities. He thinks someone has the Chronicles.”

Alex stared at him in confusion. “Who is Dr. M, why does he want a set
of chronicles, and why do you look like a big talking fox?”

The fox creature looked around. “It is not safe to talk here, we must
make for my house. It is only a short walk away.” Alex nodded. The two
walk for a while, when Alex notices something. “What's that?” He
asked, pointing to a furrball.

The fox-like creature panicked. “Keep away from it, it's dangerous”,
but Alex ignored the warning, seeing it's seemingly cute exterior and
wanting to pet it. Before he gets the chance to let it bite off his
hand, it suddenly gets stomped. Alex jumps in shock, before noticing
who defeated the furry monster. “What did you do that for? I only
wanted to pet it.” “If I let you pet it, it would have bitten your
hand off, or worse. I know where you came from, and you should know
better than to trust animals by their appearance.”

The fox companion looked at Alex and the other person. “Alex, this is
Helen, my step-daughter.” “Step-daughter? But that means...you're a
girl!?!” Admittedly, it wasn't easy to tell she was a girl at first,
having clothing that resembled Alex's wear. However, the voice should
have been a dead giveaway, as is her long, braided hair. Helen rolls
her eyes, “What? You honestly never saw a girl before?” She
asked. “Not any that looked like me, at least not since my parents...”
His head drooped as he remembered their deaths. The fox looked
cautiously. “If Furrballs are around than we must hurry. Drop your
things Alex, the sooner we get to my house the better.” Alex refused
to drop the big bag of jewels he always carried with him. Angered, a
fireball suddenly formed in Helen's fingers and she launched it at the
bag. Alex was horrified, but he didn't dare to touch the bag, not
wanting to get burned. He gave a sigh. “I guess I will have to start
all over.” He said with a sob. The three heard rustling in the
bushes. “We must go, now!” Said the fox. [/CUTSCENE]

(The second part of the tutorial level goes here) [LEVEL ENDS]

[CUTSCENE] When the last of the three enters the house, the fox closes
and locks the door. “Now we can talk in relative safety. I am
Deepak. I am the one who build the pipe that led you here. I needed
one more person to come out in order to begin the quest.” Alex
blinked. “What quest?” “To stop Dr. M from getting the Chronicles.”
Helen said matter-of-factly. “What chronicles, can someone explain
what is going on?”

“They are the Malevolent Chronicles,” answered the fox creature. “They
are the final, missing piece of his collection of literature. With
them he will have the power to rule this world...

“Malus, that is his full last name. heir to the Great Library, keeper
of books, and his Ph.D. dissertation is one of the most respected in
the land.” “Ph.D. ?” Alex asked, having lived in the jungles and
rainforests most of his life. “Do you even know what school is, Alex?”
The boy nodded his head, as if to say no. “Basically, a Ph.D. is a
piece of written writing that states that you passed a certain
standard of intelligence. It is not easy to receive one, let alone one
as respected as the one Dr. Malus has.”

Alex thought hard. “But chronicles, aren't they like stories? How can
stories be dangerous?” “There are many ways that stories can be
dangerous” the fox replied, “Some stories have dangerous ideas, others
could be used to insult others. The Malevolent Chronicles, however, is
dangerous because of the potential dark magic that can come from it.

“The Malevolent Chronicles document the quest of a man to learn great
knowledge. At least, that's how it begins. Halfway through them, he
succeeds in his quest, and in the process becomes an unrecognizable
force of evil. The rest of the Chronicles, what makes them truly
Malevolent, are the dark spells that it contains. Some of the pages
give instructions on how to awaken several great evils. Other pages
list rare animal species that could be used for evil purposes, and
where to find them.

“Legend states that after the book was completed, it developed a
horrible mind of its own. Nobody is able to prove that though, since
it has disappeared from the face of the earth thousands of years
ago...or so we thought. Dr. Malus, along with his right hand man Lord
Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon, has found evidence that the
Chronicles are buried somewhere nearby. He is using his army of
monsters to hunt the land for pages of the Chronicles. Already some of
them have been located. Dr. M must not be allowed to complete the
collection of the Chronicles. You must gather the pages and then
destroy them.”

Alex narrowed his eyes. “Has anyone stood up to this 'Dr. M'?" he
asked.

“He has an army of monsters under his command and a factory to make
more of them,” explained the fox creature. “Besides that, we Faythians
are terrified of the monsters that roam our land. You must go with
Helen, she will help you in your quest.”

“Will anyone else help me defeat this Dr. M?” Alex asked, worried that
two kids like themselves wouldn't be enough to prevent the tragedy
that is in front of them. “I have two grandsons. One of them is
willing to help you, but the other might only help you until he can
find a way out of doing so. Prewitt! Haakon!” The two twin fox cubs
come down some stairs. The former is curious as his grandfather
calling him, while the ladder was annoyed. “I want you two to help
these two in their quest.” Haakon groaned, asking “Do I have to?” “I
don't see what you're complaining about.” His brother said. “I can't
wait to fight the good doctor.” “Then go,” Deepak said, “and good
luck!” [/CUTSCENE] [END OF TUTORIAL]

Index of worlds:

\begin{enumerate}
\item Warp Zone (Optional)

  \begin{enumerate}
  \item World 1 Secret Level 3 – large switch unlocks access to
    World 2 Warp House and World 2 Shortcut to World 2 Boss. (The
    second packet of the Chronicles is hidden here.)
  \item World 3 Secret Level 1 – large switch unlocks access to
    World 3 Secret Level 2. (The third packet of the Chronicles is
    hidden here.)
  \item World 3 Secret Level 2 – secret boss \#3. (There is no
    secret boss \#2) When defeated, you have to press the large switch
    to complete the level. Large switch unlocks access to World 4 Warp
    House and World 4 Secret Level 1.
  \item World 4 Secret Level 1 – large switch unlocks access to World
    4 Secret Level 2. (The fourth packet of the Chronicles is hidden
    here.)
  \item World 4 Secret Level 2 – secret boss \#4. When defeated, you
    have to press the large switch to complete the level. Large switch
    unlocks access to World 5 Warp House and World 5 Secret Level 1.
  \item World 5 Secret Level 1 – large switch unlocks access to World
    5 Secret Level 2. (The fifth packet of the Chronicles is hidden
    here.)
  \item World 5 Secret Level 2 – secret boss \#5. When defeated, you
    have to press the large switch to complete the level. Large switch
    unlocks access to World 6 Warp House and World 6 Secret Level 1.
  \item World 6 Secret Level 1 – large switch unlocks access to World
    6 Secret Level 2.
  \item World 6 Secret Level 2 – large switch unlocks access to World
    6 Secret Level 3. (The sixth packet of the Chronicles is hidden
    here.)
  \item World 6 Secret Level 3 – large switch unlocks access to the
    middle of World 6.
  \end{enumerate}

\item The Quest Begins (Once access to the Warp Zone is granted by
  located the secret level, the second half of the world can be
  skipped)

  \begin{enumerate}
  \item World 1 Warp House – accessible after completing World 1
    Secret Level 2.
  \item World 1 Level ? – Half-way point of World 1. Large switch
    unlocks World 1 Secret Level 1, however, you can easily ignore the
    large switch and go to the next normal level. The level before
    this one has a cutscene after completion.

    [CUTSCENE] The four travelers stop to rest. It is nighttime,
    and the four made a campfire. “How much farther do we have to go?”
    Haakon whined. Helen signed. “A long way, or a short
    way. According to the map Deepak gave us, the next area contains
    what is called a warp house. However, it is well hidden, and
    apparently we need to push a switch to unlock the entrance.” “Ahh”
    Haakon replied. Alex is lying down, staring at the stars. “Helen,
    why is Haakon so grumpy all the time?” He asked without
    discretion. Haakon glares at him for a second, then goes back to
    what he was doing. Helen comes closer to Alex, so that she can
    talk softly. “I bet you were wondering where the parents of Haakon
    and Prewitt are. It happened five years ago, before I
    arrived. Like Deepak was and Prewitt is now, they were one of the
    few Faythians willing to defend themselves. One night they got
    ambushed by a cloaked figure and some monsters. They tried to
    fight back, but failed, and haven't been heard from since.” “Their
    'bravery' was more like stupidity!” Haakon replied “They should
    have stayed at home and raised us two cubs.” He tried to hide
    tears. “I don't remember them much, but what I do remember is
    their warmth and their courage. What has it got them? For all I
    know they died soon after they disappeared.” His sorrow slowly
    turned into anger. “Alex, do not mention our parents again, or
    I'll--” Helen got in between them. “Save it for the doctor.” She
    looked around. “I guess we all have something in common, our
    guardians all suffered horrible fates. We must keep moving...”
    They put out the fire and start walking toward the next level
    [/CUTSCENE]

  \item World 1 Secret Level 1 – large switch unlocks World 1 Secret
    Level 2 (The first packet of the Chronicles is hidden here.)

  \item World 1 Secret Level 2 – secret boss \#1. Defeating it unlocks
    World 0 Warp Zone and World 1 Warp House.

  \item World 1 Boss – Giant Furrball. Defeating the boss completes
    the level.
  \end{enumerate}

  \item The Disorganized Path (Once World 1 Secret Level 3 is
    completed, every normal level except World 2 Boss is optional)

    \begin{enumerate}
    \item World 2 Warp House – Accessible after completing World 1
      Secret Level 3.

    \item World 2 Shortcut to Boss – A second Warp House that, as its
      name suggests, gives access to World 2 Boss.

    \item World 2 Boss – [CUTSCENE] (You walk up to the boss area. The
      boss attacks you from nowhere, causing you to bleed a
      little. This is the only area where injury causes you to
      bleed. Alex wipes the blood off and begins to fight) [/CUTSCENE]
      When defeated, you have to press the large switch to complete
      the level. Doing so unlocks World 3 Warp House, World 3 Secret
      Level 1, and, if the level is accessed by World 2 Shortcut to
      Boss, all previous levels in World 2.

    \end{enumerate}

  \item he Borderlands (Once World 3 Secret Level 1 and World 3
    Secret Level 2 are completed, the whole world is optional)

    \begin{enumerate}
    \item World 3 Warp House

    \item World 3 Boss –Although it would be very difficult, if not
      impossible, to skip World 2 Boss, if that somehow happens than
      that boss will replace the World 3 Boss. Defeating the actual
      World 3 boss completes the level. If the World 2 Boss is
      defeated in the World 3 Boss level, access to all levels in
      World 2 is granted.
    \end{enumerate}

  \item The Great Expanse (Once World 4 Secret Level 1 and World 4
    Secret Level 2 are completed, the whole world is optional)

    \begin{enumerate}
    \item World 4 Warp House

    \item World 4 Miniboss – Gage. Occurs halfway in the
      world. Unless this level is skipped by using the Warp Zone, this
      would be the first encounter our heroes have with Gage. The
      fight is organized by Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord
      Kodon to test Gage's strength, he can't be killed in this level,
      nor can our heroes. If the level is skipped by the Warp Zone,
      then our heroes meet Gage in the real boss fight in World 6, and
      the fight is slightly more difficult as a result. Although it
      would be very difficult, if not impossible, to skip World 2
      Boss, if that somehow happens and World 3 Boss is skipped, than
      this level doesn't appear, and the save file is changed to force
      the player into the No Gage bad ending when the time comes.

    \item World 4 Boss
    \end{enumerate}

  \item The River of Sorrow (Once World 5 Secret Level 1 and World 5
    Secret Level 2 are completed, the whole world is optional)

    \begin{enumerate}
    \item World 5 Warp House
    \item World 5 Boss
    \end{enumerate}

  \item The City of the Ancients (Can't be avoided, although the
    secret levels provide an alternate route to the same midpoint.)

    \begin{enumerate}
    \item World 6 Warp House (Unlike the other Warp Houses, which are
      fairly close to either the beginning, middle, or end of a world,
      the World 6 one is on the outskirts. This means that you have to
      walk longer just to get to the halfway point. When you exit the
      Warp House, the first level you see is World 6 Secret Level
      1. While there aren't as many enemies in the World 6's Secret
      Levels compared to World 6's regular levels, the enemies are
      very difficult.)

    \item World 6 Boss – Gage. Although it would be very difficult, if
      not impossible, to skip World 2 Boss, if that somehow happens
      and World 3 Boss is skipped, than this level doesn't appear, and
      the save file is changed to force the player into the No Gage
      bad ending when the time comes. The outcome of this boss fight
      greatly determines the path of the game. Lord Ázdhôr/Lord
      Vodox/Lord Zodo/Lord Kodon is strengthening Gage by throwing him
      Giant Fruit (not normally assessable in the game) and
      Invincibility Lemons (whatever they are called.) In order to
      defeat Gage, you have to defeat Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon first. After you attack the lord a few times he
      will become weakened to the point of fleeing. At this point you
      keep attacking Gage until he becomes small. When that happens, a
      cutscene will trigger where you are to choose between killing
      Gage or Sparing him. If you spare him and decide to carry him,
      you will be taken to World 6 Secret Level 3. If you spare him
      but leave him there, you will get the Living Gage bad ending. If
      you kill him, World 8 is unlocked and you will be forced to
      undergo the Dead Gage bad ending. Although it would be very
      difficult, if not impossible, to skip World 2 Boss, if that
      somehow happens and World 3 Boss is skipped, than this level
      doesn't appear, and the save file is changed to force the player
      into the No Gage bad ending when the time comes.

    \end{enumerate}

  \item Inside the body of Gage (optional, but required for the good
    ending)

    \begin{enumerate}
    \item World 7 Exit (You leave Gage's body, and grow back to normal
      size.)

    \item World 7 Boss – Mesmo Slug. Defeating it violently ejects you
      from Gage's body, and cure him. In a cutscene, Alex manages to
      convince Gage to take them to the Great Library using a secret
      passage.
    \end{enumerate}

  \item The Great Library (Only fully accessible if you save Gage.)

    \begin{enumerate}
    \item World 8 Level 1 – The Main Entrance and the Path to the Bad
      Ending. When you get to the end of the level, Lord Ázdhôr/Lord
      Vodox/Lord Zodo/Lord Kodon will confront you. He forces you to
      surrender any packets of the Chronicles you have; what happens
      next depends on how you played the game. Although it would be
      very difficult, if not impossible, to skip World 2 Boss, if that
      somehow happens and World 3 Boss is skipped, then you get the No
      Gage ending. In it, Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon
      complains on how Alex and his friends prevented his plan from
      going into motion by avoiding those areas. Your “reward” is an
      infinite supply of Mesmo Snakes. The level doesn't end until you
      get bitten, in which the screen cuts to black. You get this
      message: “Knowing that he no longer had any opposition, the dark
      lord overthrows Dr. Malus. The people, ignorant about the dark
      lord's true nature, are fooled by his false declaration of peace
      and imprison Dr. Malus. He tries to warn the people about Lord
      Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon's treachary, but nobody
      believes him. It wouldn't matter anyway, because by that time
      the dark lord has successfully summoned the Ancients using the
      Chronicles, and the land will plunge into a darkness that nobody
      could stop.” If you get the Living Gage ending, Lord Ázdhôr/Lord
      Vodox/Lord Zodo/Lord Kodon mocks our heroes for letting Gage
      him, then has him try to kill them. Dr. M tries to stop Gage,
      but Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon kills him. With
      nothing holding Gage back, he kills our heroes. We then see
      inside Gage's skull, where the Mesmo Slug inside him eats his
      brain. Gage stops breathing as the Slug takes away the last
      breathe of life and completely takes over. His skin starts to
      become pale, and the color in his eyes disappears. Nothing
      anyone could say would have any affect on him now, as his mind
      became fully subservient to Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon. If the Lord were to somehow die, than Gage
      would die as soon as he finds out; but the Lord wouldn't
      die. Insead, he would use the Chronicles to summon the Ancients,
      and the land would plunge into darkness. The Dead Gage ending is
      almost identical to the No Gage ending, the difference being
      that instead of Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon
      complaining that you avert Gage's creation, he shows a
      combination of annoyance and mocking at the heroes for killing
      him. In all three of these endings, Cue credits and Bad Ending
      Credits Music.

    \item World 8 Secret Level 1– The Secret Entrance. There should be
      no enemies in this level. Ambient noses haunt it though.

    \item World 8 – The archive of the Malevolent Chronicles. If by
      hacking you get to World 8 without Gage in your party, the door
      will be locked, and you will get the Special Chronicle Delivery
      Bad Ending. If you have collected the 6 packets in the secret
      levels, the room will be empty. If not, then a guard will ask
      you for a six letter password, which is randomly generated each
      play-through. Each of the six regular bosses will give a letter
      of the password, so if you beat them, you are given the option
      to state it directly if you do so. If you skip some of the
      bosses through the warp zone, you have the option to guess the
      password or leave. If you guess the password wrong, the guards
      will attack you, and you will be forced to flee and play a level
      before guessing again. If you come back before you complete a
      different level, the guards will recognize you and attack
      again. After you say the correct password, the guards will
      leave. In both cases of guessing the correct password or having
      the six packets already, you will go to a room where the packets
      would be held. If you have any packets you place them there. Any
      packets you don't have would be there already, with the
      implication that Dr. M's forces have collected them. You burn
      the six packets and fight a boss. Defeating the boss will
      guarantee that you get the good ending.

    \item World 8 – True Final Level. The level can go down two
      different ways.  If by hacking you get to World 8 without Gage
      in your party,  Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon
      appears. He forces you to surrender any packets of the
      Chronicles you have, then Lord Ázdhôr/Lord Vodox/Lord Zodo/Lord
      Kodon complains on how Alex and his friends prevented his plan
      from going into motion by avoiding those areas. Your “reward” is
      an infinite supply of Mesmo Snakes. The level doesn't end until
      you get bitten, in which the screen cuts to black. You get this
      message: “Knowing that he no longer had any opposition, the dark
      lord overthrows Dr. Malus. The people, ignorant about the dark
      lord's true nature, are fooled by his false declaration of peace
      and imprison Dr. Malus. He tries to warn the people about Lord
      Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon's treachary, but nobody
      believes him. It wouldn't matter anyway, because by that time
      the dark lord has successfully summoned the Ancients using the
      Chronicles, and the land will plunge into a darkness that nobody
      could stop.” Cue credits and Bad Ending Credits Music. That is
      the Special Chronicles Delivery Bad Ending. If Gage *is* in your
      party, then you face Dr. M. You don't get the chance to fight
      him though... 

      [CUTSCENE] “It seems like you lost, doctor.” Alex says as he and
      his four friends look at the villain. “Are you going to come
      quietly?” “You may have gotten past my defenses, my boy, but I'm
      not going without a fight.” “You want to fight?” Alex asked, a
      smile curling in his lips. “I can't wait!” Gage looked nervously
      at Alex, then to Dr. M, then back and forth. “You may be younger
      than I am, Alexander” Dr. M replied,  “but the fact that you got
      this far shows how brave you really are. It will be an honor to
      fight you.” “STOP!” Gage suddenly shouted. Everyone was
      surprised, as he was never this loud before. “Is that parasite
      still in him?” Helen asked to Alex, as Gage stands in front of
      Dr. M and prevents the others from making a move at him. “It
      isn't that...I..” He tried to think of the right words. “I won't
      let you harm my 'uncle'. He... showed me...kindness...when my
      'father' ruled my mind.” Dr. M starts to tear up. The treatment
      that the boy got at the hands of Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon upset him, but now that he showed genuine
      love... “Alright...if that's what you want, I won't fight.”
      (What happens after this point depends on what happens to the
      six packets of the Chronicles) [/CUTSCENE] (In the Chronicles
      Delivery Bad Ending) [CUTSCENE] Alex thought to himself. “If he
      is capable of kindness, maybe it wouldn't be so bad to give him
      the Chronicles.” he said quietly to the others. “Are you crazy?”
      asked Prewitt. “You saw what he did to my homeland. You saw what
      he is capable of.” “Yes...I do. He may look like a dangerous,
      evil man, but what I really think he is is obsessed. His
      intelligence led him to search for this horrible document, but
      he doesn't seem like the type of man that would want to rule the
      world. He just wants to complete his collection of
      literature. In short, he is intelligent, strong willed, hard to
      understand...sound like someone you know?” Prewitt and Helen
      glared at him, but they knew he had a point. “If he is like I
      am, he might not do anything with the book. After all, we
      carried the remnants this far and we haven't been affected by
      them. I say that they will be in safe hands with Dr. M.”
      Reluctantly, the others agreed. “You want the Chronicles, Dr. M?
      You can have them.” He throws them to the doctor, who looks
      overjoyed. “You have no idea how happy I am right now. Lord
      Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon!” The others gulped,
      having forgot about them. Dr. M may not do anything with the
      Chronicles, but his lord is another story altogether. Alex
      facepalms. “What an idiot I am!” “What is it?” Lord Ázdhôr/Lord
      Vodox/Lord Zodo/Lord Kodon asked as he suddenly arrived. “The
      quest is over. We have the Chronicles. Turn off the monster
      generators. All of our forces will repair any damage that they
      did in their search, then return to the Great Library. There
      they will provide security. After that, I might become the
      “uncle” to your boy, but this time as a real family. That is all
      I have to say.” “And as for the four other terrorists?”
      “Terrorists they are not. They were concerned about me, and some
      of our behavior may have justified their cause, but they know
      better, and so do I. I will let them go home in peace.” “You
      incompetent fool! You spare our enemies, you let them get their
      lands back, and you plan on placing the Malevolent Chronicles on
      some shelf where nobody is expected to read them...ever. From
      this moment on, our partnership is terminated!” He suddenly
      stabs Dr. M in the heart. He takes the six packets from the
      doctor's cold, dead hands and takes out his packet as well. He
      combines the seven packets by pressing them together, magically
      aligning and binding the pages in the proper order. While this
      is happening, our heroes look at the doctor in sorrow,
      especially Gage. The boy looks at Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon. “I...hate you...father.” “What does it matter?”
      The dark lord asked. A force field suddenly emerges from his
      body. He goes to a specific page and recites an incantation. An
      unimaginably horrific creature appears, and the camera fades to
      black. [/CUTSCENE] Cue credits and Bad Ending Credits Music. 

      (In the good ending) [CUTSCENE] “Do you have the chronicles?”
      The doctor asks. Alex looks at him, “We burned the six packets
      that we found.” Dr. M sighs. “Perhaps its for the best. At least
      I have the one remaining packet, or at least, Lord Ázdhôr/Lord
      Vodox/Lord Zodo/Lord Kodon does. I wonder where he is now?” In
      another room, the dark lord looks at the remaining packet. He
      already knew that the other packets were destroyed, as he felt
      the presence of the Chronicles weaken. He memorized every single
      word in the remaining packet, then burns it himself, not wanting
      his enemies to read the passage. A scream could be heard as he
      does so. He walks over to the doctor, and shows surprise that he
      is talking to their enemies. “Ah, Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon. I was just going to speak to you. The quest is
      over. Your packet of the Chronicles is the only one
      remaining. Turn off the monster generators. All of our forces
      will repair any damage that they did in their search, then
      return to the Great Library. There they will provide
      security. After that, I might become the “uncle” to your boy,
      but this time as a real family. That is all I have to say.” “And
      as for the four other terrorists?” “Terrorists they are
      not. They were concerned about me, and some of our behavior may
      have justified their cause, but I think they are willing to
      forgive and forget. I will let them go home in peace.” “You
      incompetent fool! You spare our enemies, you let them get their
      lands back, and you let these mere kids destroy the greatest
      piece of literature ever written! From this moment on, our
      partnership is terminated!” He suddenly stabs Dr. M. Our heroes
      look shocked as the doctor collapses. Gage looks at Lord
      Ázdhôr/Lord Vodox/Lord Zodo/Lord Kodon in sorrow and
      anger. “I...hate you...father.” “What does it matter?” The dark
      lord asked. A force field suddenly emerges from his
      body. “Congratulations! You have ruined my plans for this stupid
      planet! Now there are secrets that will never be uncovered,
      entities that will never be contacted. I will let you leave the
      Great Library, but not unscathed. Prewitt! Haakon!” The fox
      twins look at each other, each wondering how he knew they
      names. “You are probably wondering how I know your names. I know
      all about you. I know about your grandfather, who put you kids
      up to this horrible quest! I also know where your parents are.”
      “Huh?” Haakon said to himself. “Don't listen to him!” Prewitt
      said. “He is probably messing with us.” “I assure you that I am
      telling you the truth. Come!” Two adult Faythians of opposite
      gender walk up to the dark lord. “No...” The twins say in
      unison. “Yes, they are your parents. Thanks to the Mesmo Slugs,
      which you should be familiar with, I managed to get information
      about the two of you and your step sister. They told me
      everything they knew. As I have no need for them now...” He
      points to a lava pit not far away. “I will have them kill
      themselves. It would be a pleasure to see you two utterly
      broken.” The two adult foxes turn around and slowly walk toward
      the pit, with mesmo slugs on their necks. Haakon looses his cool
      and runs toward his parents with a sword, attempting to slice
      off the slugs. As he does so, Lord Ázdhôr/Lord Vodox/Lord
      Zodo/Lord Kodon starts throwing red balls of energy at him. He
      manages to dodge most of them, but just as he slices off the
      slugs, he gets hit in the legs, causing great pain and crippling
      him. The three of them collapse on each other. “Of course, they
      didn't say that one of you was an idiot.” He then looked at all
      of them. “I should probably kill you all now, but I am on a
      tight schedule, and I doubt that any of you will survive what
      happens next!” He then vanishes in smoke. Nobody speaks for a
      few seconds. “Well, I guess he was too scared to fight us!” Alex
      said. “No.” Gage replies. “He has other things on his mind. When
      I was under his power, he sometimes talked to himself about what
      he was to do with the chronicles. He was hoping to release the
      Ancients and have them wreck havoc over the earth. He wanted the
      earth...destroyed.” Alex, Gage, Helen, and Prewitt looked really
      glum. The two fox parents suddenly moan and get up. “Haakon...is
      that you?” The female fox asks. The injured fox child looks
      weekly at his parents. “Mom?” The three foxes hug each
      other. The parents then notice Prewitt and hug him. “How much do
      you remember?” Prewitt asked. The male adult fox starts to
      speak. “...Everything. Whenever we were asked a question we
      always answered it, regardless of whether we wanted to or
      not. We longed for the day when our minds weren't oppressed, and
      it has finally arrived, but has it been too late?” Gage looks at
      them. “You had a life before you were infected. I...am not sure
      I had one.” “We have to get to a place of safety” the female
      adult fox said. Haakon's parents carried him as they ran toward
      the direction of the nearest safe house.  “We made it this far.”
      Helen says. “We faced the monsters of Dr. M, we got through the
      City of the Ancients, we destroyed the spirit of the
      Chronicles. I think that no matter what happens, we will be
      ready for it. The others smiled, even Gage. They suddenly hear
      noises of the monsters. “Before we do anything else” Alex
      said. “We need to turn off the Monster Generator. The four of
      them run in the direction of the Monster Generator. The camera
      points to where Dr M was stabbed. He isn't there. The camera
      fades out. Text reads “To be continued in Campaign 2”
      [/CUTSCENE] Cue credits and Good Ending Credits Music.
    \end{enumerate}
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
