\documentclass{gd-document}

\usepackage{xspace}

\newcommand\DrM{Dr.\,M.\xspace}
\newcommand\Azdhor{Lord Àzdhôr\xspace}

\newcommand\level[1]{\textit{#1}}

\begin{document}
\title{Second Proposal for a TSC Story}
\author{Marvin Gülker (Quintus)}
\date{2018-08-19}
\docnr{18/1}
\abstract{\noindent
  This is my second proposal for a storyline in TSC. It addresses
  earlier criticism, but stays true to the main concept of the first
  proposal (DNr. 16/4): It features \DrM as
  the antagonist of the player, who finally realises his mistakes when
  his Right Hand \Azdhor betrays him. Includes a suggestion on a
  heroine.}

\maketitle{}

\tableofcontents

\section{dramatis personae}

\subsection{Alex}

The hero of the game, at least on the beginning. Somewhere around 20
years old. At the beginning of the game, he is a treasure hunter
without a nearer family.

\subsection{Alice}

Heroine of the game; appears first in World 3, becomes playable in
World 4. Most of her family has died during a military conquest of
\DrM (who wanted both to find a volume of the Chronicles and paralyse
his enemy Thomas Albin), except for her grandfather Thomas (see
\ref{sec:thomas} below), with whom she lived before he sent her out
for defeating \DrM’s quest for the Chronicles. About the same age as
Alex.

\subsection{\DrM}

\DrM is the antagonist of the game. He is an old man of originally
nobel character, but has a burning desire for knowledge. He is the
heir and Protector of the Great Library, and in search of the Secret
Chronicles which he believes to be the route to complete wisdom. After
he collected 3 of the 12 volumes of the Secret Chronicles, the evil
aura of these works makes him ruthless in his quest, kicking out of
his way whomever he deems to be against his search of wisdom.

\subsection{\Azdhor}

He is the Right Hand of \DrM. An arch-evil enemy who stops for nobody
and nothing to reach his goals. He has observed that the owner of the
Secret Chronicles is the possesor of great power that can be used to
rule over everyone. He joined \DrM only to have him and his influence
help him to find the Chronicles, and he is secretly planning to
overthrow \DrM as soon as all volumes of the Chronicles are found.

\DrM does know nothing about \Azdhor’s secret plans and believes him
to be truly loyal, albeit a little rude.

\subsection{Gereon}

An old mage, friend of Alex.

\subsection{Thomas, Count of Albermore}\label{sec:thomas}

This person never actually appears in the game. He is owner of a great
area of land, and is perceived by \DrM as his main enemy. He is an old
man unable to walk on his own and a distant relative of \DrM, and long
ago one of his (and \DrM{}’s, i.\,e. before the family branches divided)
ancestors once was the Protector of the Great Library. In his family,
the danger of the Secret Chronicles has been preserved and as soon as
he noticed \DrM{}’s quest for finding the Chronicles, he sent out the
last heir of his family, Alice, to counter \DrM{}’s intents, by
collecting the volumes of the Chronicles and destroying them.

\subsection{Fayath}

A friendly fox people. Villages or or lone samples of these people can
be found all over the world. The Fayath help the protagonists where
they can: by giving hints for secrets, granting them powerups or
scrolls, or just by giving tips on the gameplay. They don’t occur
before World 5, because they’re opposed to \DrM.

\section{The scene}

A fantasy land, developed somewhere between the Middle Ages and the
Industrial Age. People know what machines are, but their use is rather
rare; government is formed by a king still, but the time of knights is
definitely over. There is a basically working police and court system
in place.

There exists magic in this world, but not known by many people and
generally its use is forbidden.

The capital of this fantasy land is Albermore. Outside of cities,
monsters like furballs, armys, etc. endanger the land.

\DrM is not the ruler of this land and he has nothing to do with its
King. He’s someone acting behind the scenes. However, using the power
of the Chronicles, he is able to silently control monsters and/or
create new monsters, which is the reason why recently an increased
number of monsters has been perceived by the people of this fantasy
land.

\section{Story}

\subsection{General Notes}

During the story, several references to well-known literature should
be made. \DrM is quoting Shakespeare all the time, and at sites like
the City of the Ancients one could make some subtle references to the
Ilias or even Gilgamesh. There shouldn’t be blatant copies, though.

Notice the frequent appearance of the number 12. 12 worlds, 12 levels,
12 volumes. This is intentional as 12 is a number used by a good
number of mythologic tradition.

\subsection{Prologue.}

[cutscene]
Alex is a treasure hunter. He searches old ruins, lost forests, old
swamps and similar areas for lost treasures to sell at high
prices. His business is not illegal, as there’s a law in this world
that says that who finds a treasure lost for at least one hundred
years gains ownership of it.

One day, he’s exploring the Eastern Desert. He finds his way through
the stony lands, climbs the sandy dunes and fights the sand storms
haunting the desert. Using an ancient map he found in a library, he
forces his way from well to oasis and to well again. Withstanding the
cold night and the burning day, he finally discovers the pyramid he
has been searching for. “So it’s true…” he said. “That old man wasn’t
lying when he talked about the golden rubies and the lost pyramid.”
He enters the pyramid, avoids its dangers and finally reaches the
forgotten Pharao’s grave chamber. However, the depth of his disgust as
he discovers the chamber to not contain a single jewel is
infathomable. All that is there is an old blue book\footnote{This the
  book of narcism.}, written in a
script he does not understand. “At least it’s richly ornamented”, he
remarks and takes the book with him as the replacement for what he did
not find. Half on his way out, he notices strange noises; like the
tapping of feet and mourning voices. Passing a corner, he sees himself
confronted with a standing mummy, glaring at him and stretching out
its arm. Paralysed by horror, he cannot move. The mummy utters: “GIVE…
BACK… THE… BOOOOOK…”, and having recovered from the shock, he runs away for
his life and escapes the deathly pyramid as more and more mummies
gather to hunt him.

Weeks later Alex has returned from the Eastern Desert to his home in
Albermore and has buried the unholy blue book deep below his other
belongings. Several times he considered getting rid of it, but the
fact that it somehow invoked the mummies in the pyramid back to life
still leaves him too curious. Returning from a visit in Albermore’s
library, he finds a message pinned at his home’s door with a
knife. “Come to the corner between Church Street and Salt Street this
night at 1. Bring the Chronicles if you value your life.”. Inside,
everything has been turned upside down, but the secret door where he
kept his treasures including the book (which he concludes to be the
“Chronicles”) had not been found.

There’s no such thing as angst in a real treasure hunter (except if
faced by living mummies, perhaps), so instead of complying he ventures
outside at night and waits for the person to come to him
instead. However, instead of this person, several policemen appear
early in the morning when everything is still dark. It quickly becomes
clear that someone had given the police false clues about some capital
crime and they were now after arresting him. Knowing that it could
take a very long time to get released even if innocent, he decides to
hide instead. Given that this book must be of utter importance for
this unknown person if it even sets the police to his heels with false
clues, he wants to know more and possibly make a good deal with it. He
decides to visit Gereon, an old mage who has always been interested in
mystic stuff and exercises the forbidden practise of magic. When the
police discovers his hiding, he attempts to escape and heads hastily
towards the forest outside of Albermore, which is where Gereon lives
deep inside.
[/cutscene]


\level{Level 1. Flight.}

A city level with mild time constraint. Alex wants to escape the
police forces. The level ends at the edge of the forest.

\level{Level 2. Forest.}

Alex on his way to Gereon’s hidden home in the forest. Level ends
there.

[cutscene]
Alex shows Gereon his mysterious book, but Gereon cannot make much of
it. After some thinking, he tells Alex an old story he has heard of
during his journeys, in which there are 12 books of the Secret
Chronicles, who set their owner into the ability of gaining absolute
knowledge about the world. It might be possible they even include the
key to eternal life, however, the books, if collected in larger
amounts, are said to have an evil aura influencing their possesor
towards the evil. Thus, the Ancient People who has wrote these
Chronicles has decided to hide them separately all over the land,
such that they might only be found when the time has come mankind can
handle them. For the time being, they erected the Great Library, place
of eternal wisdom, whose Protector has knowledge about the hiding
places and has the duty to shield mankind from the Chronicle’s
influence until the time has come. Ages have passed since that time;
the Ancient People is extinct (only ruins of their city exist), and
about the Great Library there are only rumours left. The only hint
given in the story is that the Great Library is hidden deep in the
southern jungles of the land.

Alex is baffled by the story he has innocently been drawn into. Now
he likely has one of those twelve Chronicles in his hands, a dangerous
tool for mankind. His intention to sell it to the person who requested
it has vanished; it is likely that this person has no good intentions
with that powerful tool. Instead, he decides, the book must be brought
to the Protector of the Great Library. Gereon wishes him good luck,
and to circumvent the police still in search for Alex, he shows him a
secret tunnel that leads outside the forest.
[/cutscene]

[ Actually, the person requesting the book was \DrM. This is not
mentioned explicitely from the story, but becomes clear from what
happens. ]

\level{Level 3. Tunnel.}

Simple underground level ending with an exit outside the forest.

\subsection{World 1. The Jungle.}

The world features jungle levels and could include native
mythology.

\level{Some jungle levels here. Later levels with bookshelves
  somewhere, to indicate Alex is reaching the Great Library.}

\level{Last Level. The Great Library}

A short jungle period, then the path widens and Alex stands before the
main entrance of the Great Library.

[cutscene]
Alex is asked for what he wants at this secret place nobody knows. He
reveals his possession of one of the volumes of the Chronicles,
resulting in him being taken through the main entrance and some
corridors directly to \DrM{}’s working room.

At his first enountering with \DrM, \DrM acts as a nice person. He
introduces himself as the Protector of the Great Library and
explicitely thanks Alex for his efforts to bring the volume to him. He
confirms that the story of the Ancients, the Library, and his
protection duty is true and further elaborates on the topic. “The
Chronicles are comprised of twelve volumes that describe the quest of
a man to learn great knowledge. On his journey, he learns how to
understand, summon and control the deepest affections of mankind:
malevolance, hatred, envy, greed, narcism, but also benevolance, love,
admiration, justice, and courage. Each of the first ten volumes is
said to describe one of these attributes in detail. The two remaining
volumes are the book of spells and the book of creatures, these
documenting the mightiest magic spells and the secret of life.” \DrM
then notes he has already been able to find three volumes\footnote{The
  books of malevolance, of courage, and the book of creatures, the
  latter setting him into position to create all these monsters.}  and
tells Alex that for best execution of his duties he needs to obtain
possession of all 12 volumes\footnote{In reality, the 3 volumes \DrM
  has obtained already have infected his mind. He has become a man
  striving for the absolute wisdom, believing that he is the saviour
  of mankind if he manages to find and understand all the
  Chronicles. Anybody who is standing in his way gets eliminated. At
  this point, he just thinks Alex can be of use for him, so he tries
  to include him into his quest.}. He finishes with some fitting
Shakespeare quote.

\DrM also talkes about the Count of Albermore, whom he depicts as his
enemy. He makes Alex think that this person wants to obtain the
volumes just for the sake of power and subjugation, and that he has to
be aware at any time that spies of the Count might try to convince him
from the contrary.

Lastly, \DrM introduces him to \Azdhor, his Right Hand and tells him
to hand any volumes he finds to him if \DrM himself is not reachable
at that time. Alex finds \Azdhor very, very unsympathic from the very
beginning.

\DrM now sends out Alex as his agent in the quest for searching the
Chronicles.
[/cutscene]

[\DrM 4 volumes, Alex 0 volumes]

\subsection{World 2. The Expanse}

An ordinary world with nothing really surprising. Unpopulated areas,
with many elements ranging from deserts to frozen tundra to forests to
plains.

\level{Several levels...}

Last level ends with finding another volume, the book of admiration.

[\DrM 4 volumes, Alex 1 volume]

\subsection{World 3. The Mountains}

The mountain world features some castle levels and several outdoor
hill/mountain levels.

\level{Several levels...}

After the last level’s boss, Alex finds another volume, the book of hatred.

[cutscene]
Before he can leave, Alice appears. She is too late, as Alex has
already set himself into position of the volume. A dispute arises
where she identifiers herself as being sent by the Count of Albermore
and tries to convince him from \DrM{}’s real intentions. Remembering
\DrM{}’s warnings against the Count, he does not believe her; before the
dispute can continue, \Azdhor shows up and attacks Alice, who flees. He
asks Alex rudely to hand over the two found volumes, and after having
received them, he sends him to the City of the Ancients, where he says
\DrM expects another volume to be hidden.

[\DrM 4 volumes, \Azdhor 2 volumes, Alex 0 volumes]

\subsection{World 4. The City of the Ancients.}

This world is the turning point in the story. It also features the
Return of the Mummies™, this time as real enemies in the levels, but
with the same effect as in the prologue: facing a living mummy up
front paralyses the protagonist for a short amount of
time\footnote{Actually, an idea taken from the Zelda series.}. Mummies
however cannot be defeated. You need to get around them somehow. As
enemies, they don’t move at all or only very slowly in direction of
the player. If you touch a mummy, all energy is drained from you
except for the last bit. If you touch a mummy with the last bit, you
are killed\footnote{This refers to the energy system that will later
  be introduced.}.

The City of the Ancients is located deep in the southern jungles (no
coincidence that the Great Library is located there as well). Ruins
that have been overgrown by jungle plants. The City of the Ancients
itself however resides on a plateau with only bare vegetation so it
can be depicted as vast and empty. It is intended that the City itself
is comprised of several levels.

\level{Level 1-4 normal jungle levels}

\level{Level 5-8 City of the Ancients levels.}

\level{Level 9. The Ancient Temple.}

[cutscene]
At the end of this level, in a catacomb where nobody can
escape easily, Alex meets Alice again. This time, Alice tells him about
the military conquests \DrM has done in search for the Chronicles, and
in tears reports the death of most of her family as a result. Alex
this time believes her, and from this point on both strive to stop
\DrM. Alex feels miserable as he recognises his mistake.

She tells Alex that \DrM has not been successful with his conquest
against her family; the two volumes in their possession have been
hidden by the Count in his younger years. She knows the hiding places,
but there is also a strong hint that one volume never left the City of
the Ancients, which is confirmed by \Azdhor{}’s command to Alex to
search for it here.
[/custcene]

[ At this time, both believe \DrM has now obtained possesion of 6
volumes. In reality \Azdhor never handed the two volumes he got from
Alex to \DrM, \DrM does not know that. That is, \DrM at this point
still has only 4 volumes. ]

\level{Further levels, with the book of spells being found at the end of
  the last level.}

[\DrM has 4 volumes, \Azdhor 2, Alex and Alice 1 ]

\subsection{World 5. Riverland.}

This world introduces the Fayeth. The fox people usually avoids human
contact as it often has had bad experience with humans. They suffer
from the increased number of monsters as they don’t have as effecive
defensive measures as human cities like Albermore; instead, they
prefer to hide their villages up in trees, deep in caves, on islands
on lakes, and similar. This world has the highest amount of Fayeth of
all worlds in the game.

The Riverland is full of secret switches that need to be activated to
open the path to the Great River Cave, where the volume of this world
is buried. Consequently, not all levels can be completed by just
trying to play though them because to reach the next platform, open a
locked door, or to overcome similar obstacles, the player needs to
find the corresponding secret switch. For this however, the player
receives clues from the Fayeth in earlier levels and of course in the
Island City of Fayeth where most Fayeth live.

There are many rivers in this green and fresh world, and neither Alex
nor Alice can swim!

\level{Several levels.}

[cutscene]
At the last level, they encounter \DrM who just set himself into
posession of the volume of this world, the book of envy. He immediately notices Alice
next to Alex and understands he lost his influence on Alex. With
\Azdhor protecting him, he leaves, indicating in a half-heard sentence
something like “I will get the three volumes you still have as
well!”.

[ This is a hint that \DrM thinks the two volumes \Azdhor has are
still with Alex and Alice. ]
[/cutscene]

[ At this point, \DrM has 5 volumes, \Azdhor 2, Alex and Alice 1 ]

\subsection{World 6. Western Desert}

The corresponding point to the Prologue’s Eastern Desert. Hot and
dangerous, with quicksand and similar obstacles, with pyramids and
catacombs. A lone Fayeth somewhere gives a tip like “you can escape
quicksand by repeatedly trying to jump in high frequence”. Obviously,
the lovely mummies are just waiting in these levels to scare our
heroes.

\level{Regular levels, with the book of benevolance being found at the end.}

\level{Level 3, Oasis Village.} A small village built at the place of
an oasis. In the level there’s a sign with a “WANTED:” advertisement depicting
Alex. If the sign is read, it runs: “Wanted: This person
that calls himself “Alex” is highly suspective of murdering the
industrial Glenn Woods. He is described by the main witness as
follows: … (\DrM describing Alex, of course including some Shakespeare
quote)”. This kind of sign can be added to later levels and worlds just for
decoration as well.

After this world’s boss, a volume is found. It is the book of
benevolance.

During the course of this world (but not narrated; it can be concluded
from what happens next) \Azdhor finds another volume (the book of
greed) and hides it in the Monster Factory, which is basically for him what the Great Library
is for \DrM: The main operation point.

[ \DrM: 5 volumes. \Azdhor 3, Alex and Alice 2 ]

\subsection{World 7. \DrM{}’s ship.}

Starting probably with water levels\footnote{There was a scuba suit
  requested on our tracker.} the protagonists quickly reach \DrM{}’s
ship, a technically advanced ship that contains monster production and
is often used by \Azdhor for travelling. Given the ship is property of
\DrM, Shakespeare quotes can be found on it (and of course, the ship
itself is named “Tempest”, which should be shown on a graphic somewhere).

\DrM{}’s ship is a modern ship, featuring mecha enemies. While the
setting is similar to the Monster Factory (World 9), it’s not as
intense.

\level{Regular levels.}

The boss of this world is \Azdhor. When defeated, however, he
escapes. After the boss fight, they find \Azdhor{}’s two volumes,
i.e. those that Alex earlier handed to \Azdhor.

[cutscene]
The ship sinks after receiving the volumes.
[/cutscene]

[ \DrM: 5 volumes, \Azdhor 1, Alex and Alice 4 ]

\subsection{World 8. Cave system}

The world of caves, large and small. Occasionally a grave with
mummies. Occasionally dark levels that require careful use of Alex’
flashlight.

\level{Regular levels.}

\level{After Level 8.} [cutscene]The 4 volumes collected by Alex and
Alice show the evil influence effect on them, strengthened by the
darkness of the caves. Both accuse each other for being too
slow with regard to \DrM taking the volume at the end of World
5. Alice suspects Alex to be influened still by his own earlier
meeting with \DrM, while Alex begins to doubt the Count’s position and
asks whether the Count does not really have own plans. The dispute
remains unresolved.[/cutscene]

At the end Alex and Alice find that the volume hidden here, the book of
justice, is gone. \DrM has been here earlier. Instead of the book,
there’s a sarcastic letter from \DrM mocking at them.

[cutscene]
Blaming is taken to a new level. Now they suspect each other to
actually want all of the Chronicles. After a short fight, the two
divide, each one with 2 volumes.
[/cutscene]

[ \DrM: 6 volumes, \Azdhor 1, Alex 2, Alice 2 ]

\subsection{World 9. The Monster Factory.}

Alex and Alice each play different levels in this world. Since this is
not possible technically in this way currently, it can be simulated by
an ordinary world path with the levels alternating the character,
i.e. level 1 is played by Alex, level 2 by Alice, level 3 by Alex
again, level 4 by Alice, etc.

The hightech factory has mecha enemies just like \DrM’s ship (World 7), but has
an even more heavy focus on modern technology. It should be made clear
that neither Alex nor Alice actually understands what is happening
here.

\level{Level 1. Assembly Lines.} Various kinds of monsters are assembled on
conveyor belts using robotic systems.

\level{Level 2. Waste Disposal System.} Factory waste is processed and purged
here.

\level{Level 3. Elevator System.} A mechanized, high tech elevator system.

\level{Level 4. Control Center.}

\level{Level 5. Factory Operations.} Oversees running of the factory.

\level{Level 6. R \& D (Research and Development).} Oversees the development of
  new technologies. Includes genetics and/or magic research: Oversees
  the creation of new monsters, weapons, and other
  technolgies. Includes Super Computing Station: Mathematical
  simulations and other data crunching are executed here. The outside
  room is filled with computer monitors showing data/scientific
  visualisations.

\level{More levels.}
  
[cutscene]
Alex and Alice reach the boss level simultaneously. With only 2
volumes in possession for each of them, the evil influence weakened,
and the two unite again.
[/cutscene]

\level{Boss level.} [cutscene]\Azdhor appears and ironically
congratulates that Alice and Alex to have made it that far. He says
that while it would be a pleasure for him to eliminate them, he is
busy and needs to visit \DrM. Then he says: “You two should give
up. \DrM now owns six volumes, and with the one I have here and the
one somewhere still in Albermore, he will have the majority of the
Chronicles. You cannot withstand them.” “We do!” “Do you? I'm sorry to
inform you that your journey has just terminated right here. Let me
show you the power of the Chronicles of Greed!” \Azdhor targets Alex
and summons a dark and mindless copy of him. “Engage the enemy, Alex!”
he shouts and disappears. With the glowing Chronicles book in the
background (it has no function, it’s just decoration), the clone just
says “…GAGE…! I… WANT… THE… CHRONICLES!”, attacks and the battle
begins.[/cutscene]

This is a difficult boss and both Alice and Alex are present
simultaneously; the player can change control by running into the
respectively other character (collision). Only by combining Alice’ and
Alex’ different capabilities, the boss can be defeated. With the last
bow, the dark clone just vanishes and the Chronicles volume stops
glowing.

After the boss \Azdhor{}’s volume, the Book of
Greed, is taken.

[ \DrM: 6 volumes, \Azdhor 0, Alex and Alice 5 ]

\subsection{World 10. Albermore.}

The quest ends where it started. In multiple levels in this world the
police shows up again and tries to arrest Alex, while they search
through several buildings in the city for the last volume.

\level{Level 1-5, some are time levels as Alex and Alice escape the police.}

\level{Level 6. In this level, Alex gets finally arrested by
  police, but all volumes are with Alice. She must play alone the next levels.}

(Note: This at least compensates a little for the Alex-only part at
the beginning of the game).

\level{Level 7-9. Normal levels.}

\level{Level 10. The Museum of History. In this museum, Alice finds the
  last volume without a boss fight, the book of love.}

[cutscene]
With 6 volumes, one would expect the evil influence to take Alice
over. When she however remembers \DrM{}’s military campaign, she withstands the
pressure. Not noticed positively by her, however, she got some help
from the book of love she just found, which does have its very own influence…
[/cutscene]

\level{Level 11. Free Alex! Tunnel level leading to the arrest cells
  of the Albermore police station. Level is played both forward (Alice
  alone) and backward again (now with Alex and Alice).}

[cutscene]
\DrM at the police station, looking at the escape tunnel, very upset.
[/cutscene]

[ \DrM: 6 volumes, \Azdhor 0, Alex and Alice 6 ]

\subsection{World 11. The Great Library.}

Alex and Alice return to \DrM{}’s base with the intention to rescue the
volumes owned by \DrM. It is obvious they can’t enter through the
well-watched main entrance as Alex did when he first arrived here, so
they make for a side entrance.

The Great Library is a vast building with three floors and several
rooms. The floors are connected with an old-fashioned elevator system
(“paternosters”) with minimal electric systems (if any at all). The
levels of this world show different parts of the library.

\level{Level 1. Defense Station.} A level between the outer wall of
the library’s ground and the library building itself. Many monsters to
fend off intruders.

\level{Level 2. Side entrance.} Continuation of level 1 that ends at a
side entrance of the library.

\level{Level 3. Ground Floor.}

\level{Level 4.} Rooms where \DrM can invite guests, the dinning room,
kitchen, etc.

\level{Level 5. First Floor.} All the books.

\level{Level 6. The stacks.} Floor after floor with column after
column of even more… BOOKS.

\level{Level 7.} Any more books.

\level{Level 8. Second Floor.}

\level{Level 9.} You know what? Books!

\level{Level 10.} Third floor. Rooms filled with paintings,
chandeliers, and a balcony by which \DrM can oversee the land below.

\level{Level 11. The Chronicles Room.} In this room \DrM keeps his
volumes of the Chronicles. Alice and Alex take them all and feel a
little strange about this now.

[ \DrM: 0 volumes, \Azdhor 0, Alex and Alice 12 ]

\level{Level 12. \DrM’s working room.}

Expecting the great showdown.

[cutscene]
Alex and Alice enter \DrM{}’s working room. Both \DrM and \Azdhor are
there, debating over the topic of the volumes. Alex and Alice show
they’re in possession of all 12 volumes. They demand that the two give
up and leave the library immediately. Now something unexpected
happens. \Azdhor realises that \DrM is of no use anymore for him. He
takes him as hostage and threatens to kill him if he is not handed the
Chronicles. \DrM is completely surprised, but unable to defend due to
his age. Alex and Alice hand
the volumes over finally. \Azdhor frees \DrM and leaves the library.

[It is implied that Alex’ and Alice’ possession of the full 12 volumes
is only for such a short amount of time that there’s no opportunity
for their evil aura to take them over]

\DrM is heavily shocked about what has happened. He realises the
Chronicles are gone, and are with \Azdhor. Sinking into a nearby chair
he slowly thinks through all that happened during his quest for the
Chronicles, and that now, in the last moment, he has been betrayed by
a person he truly believed to be loyal to him. Long silence.

Finally \DrM approaches our heroes. He announces that he from now on
will live up to the duty has has as the Protector of the Great
Library, and that he was tempted by the Chronicles. He assures he will
never again fall into this temptation, and says that it now is on him
to prevent the evil \Azdhor from causing severe damage with the
Chronicles. He reveals that the Ancient language that Chronicles are
written in has not yet been entirely deciphered by him and \Azdhor, so that
there is some time left to stop him. Furthermore, he says that he
expects \Azdhor to have returned to his cloud castle, where they must
now go.
[/cutscene]

[ \DrM becomes playable at this point ]

\subsection{World 12. Cloud world.}

\level{Level 1. The Staircase Tower. A level with many, many, many
  stairs.}

[cutscene]
The cloud world is gone, and with it is \Azdhor{}’s cloud
castle. \Azdhor, by the power given by the Chronicles, opened a magic
portal to a new dimension and transferred his castle there. Taking
together all courage, Alex, Alice and \DrM enter the portal and find
themselves in a dark cloud world in a redish burning sky full of enemies never seen before.
[/cutscene]

\level{Cloud levels...}

\level{Level 12. The Cloud Castle.}

This level has \Azdhor as the final boss; special dramatic final boss
battle music plays here. The battle has two stages and is special in
so far as all three playable characters are present simultaneously
(control switch as with World 9 boss). Only by combining the abilities
of all three characters, it is possible to defeat \Azdhor on the first
stage.

[cutscene]
When defeated however, \Azdhor throws open a bookshelf door and from
the open door emerge the 12 volumes of the Chronicles. They revitalise
\Azdhor and the second stage of the battle begins. Music change to a
spheric, irrational variant of the stage 1 music.
[/cutscene]

The volumes, each glowing in a different color, fly through the room
and attack by flying against the currently played character. \Azdhor
himself cannot be defeated again while the volumes are there, only
paralysed. During \Azdhor{}’s paralysis, the volumes stand still and \DrM
has to cast a special fire spell on as many volumes as he can while
\Azdhor is paralysed. If a volume takes a hit from that spell, it is
immediately destroyed by the fire and releases something that
corresponds to its content (e.g. life berries from the book of love or
some small enemies from the book of malevolance).

[cutscene]
Once all volumes are destroyed, \Azdhor dies in mysterious green-black flames. The
cloud world is moved back to the real world, the portal closes, and
the protagonists find themselves deep in the jungle in the ruins of
something that must ages ago have been the Great Library…
[/cutscene]

\subsection{Epilogue}

Back in Albermore, Alex again gets arrested by police. \DrM, who in
the first place caused the persecution by his false clues, admits this
so that Alex must be released finally. It is hinted that Alex and
Alice continue a not-really-peaceful life as a treasure hunter
couple, still chased by living mummies every now and then.

\section{Changes since Version 1}

\begin{itemize}
  \item Responses to criticisms and other proposals:

    \begin{itemize}
    \item Alex is now a treasure hunter instead of a thief,
      following datahead’s suggestion. This was probably the main
      criticism.
    \item Akan was renamed to “Alice”, following Bugsbane’s
      suggestion.
    \item \DrM{}’s much criticised death at the end was removed.
    \item No press for story advancement. This addresses kirbyfan’s
      concerns.
    \item The Albin family lost its last name. “Counts of Albermore”
      suffices. This addresses datahead’s criticism of the naming.
    \item The Chronicles’ volumes have been given attributes as
      suggested by datahead. Likewise, instead of doing nothing as in
      the first proposal, each has a special effect. datahead’s magic
      realm suggestion was combined with my cloud world proposal.
    \item The Fayath were introduced as a “good” fox people as was
      suggested by both danfun and datahead in their respective
      proposals. The naming comes avoids Bugsbane’s criticism of
      resembling “faith”.
    \item The levels from datahead’s proposal have been
      included. Skyscrapers were skipped, since Bugsbane has a point
      with them not fitting the theme.
    \item Gage from danfun’s proposal has been included, albeit in a
      much weaker form and not as a story element. danfun’s Mesmo
      species is too dark for TSC to include.
    \item Hints on the contents of the Chronicles were added (taken
      partly from danfun’s proposal and partly datahead’s suggestions,
      mixed with my own ideas).
    \end{itemize}

  \item Other changes:

    \begin{itemize}
    \item Introduction of the mummies.
    \item The police now hunts Alex because \DrM has made them believe
      that Alex is a criminal, albeit he isn’t.
    \item The Chronicles now form part of the final boss fight against
      \Azdhor and are destroyed thereby by the player.
    \item The Chronicles now have an evil influence on the heroes as
      well.
    \item More details on levels.
    \item Gave the remaining unthemed worlds themes and explained the
      existing themed world’s setting in more detail.
    \item Made Alex and Alice a couple in the Epilogue, with hint in
      World 10.
    \item Several smaller changes.
    \end{itemize}
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
